Contention Management for 5G

### 2017-02-13 article/article.tex
algobrute
merge

	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and
	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
	%Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$. Dominique voulait être plus général, on mettera cette propriété dans notre topologie

@@

      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
      The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.

@@

      \noindent {\bf Input:} a routage graph $\cal R_{\cal C}$, an integer $\tau$ and an integer $P$.

      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R_{\cal C}$ ?

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.

      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any odd $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}

      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network

      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
       We have as much BBUs as RRH in the network. We denote by ${\cal c}$ the size of $S$ and $L$, and so, the number of routes.
       We are given a period $P$, a routing function ${\cal R}$, and an assignment ${\cal C}:L\rightarrow S$  which assigns a BBU to each RRH. 
       $l_i,i<{\cal c}$ is the RRH of the route $i$ and ${\cal C}(l_i)$, or $s_i$ is its corresponding BBU. The routing between each RRH and BBU is given by the routage graph ${\cal R}_{\cal C}$.

       Let consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_l$ to 
      $(l,{\cal C}(l))$ and $m_{{\cal C}(l)}$ to $({\cal C}(l),l)$.

%       
%       We denote by $n$ the size of $S$ and $L$. We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH. Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$. Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to 
%       $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.

@@

      This message is received by ${\cal C}(l)$ at time $t({\cal C}(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{{\cal C}(l)}$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$, otherwise at time $m_{{\cal C}(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{{\cal C}(l)} - t({\cal C}(l),r_l)$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$ and $w_l = m_{{\cal C}(l)} + P - t({\cal C}(l),r_l)$ otherwise.

@@

%       \begin{center}
%       \includegraphics[scale=0.2]{rrh.jpeg}
%       \end{center}
%       
%       This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
%       
%        \begin{center}
%       \includegraphics[scale=0.2]{BBU1.jpeg}
%       
%       \includegraphics[scale=0.2]{BBU2.jpeg}
%       \end{center}
%

@@

      Thus, the whole proccess time for a message sent at vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{{\cal C}(l)}).
      $$

    The {\bf maximum process time} of the $(P,\tau)$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.

@@

      \noindent {\bf Input:}  A routage graph ${\cal R}_{\cal C}$, a period $P$, an integer $T_{max}$.

@@

    \node (2) at (-7,0){\Huge H};
    \node (3) at (10,0){\Huge G};
    \end{tikzpicture}

>>>>

  \todo{Remplacer Dl par dl}

	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
	%Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$. Dominique voulait être plus général, on mettera cette propriété dans notre topologie

@@

      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
      The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.

@@

      \noindent {\bf Input:} a routage graph $\cal R$, an integer $\tau$ and an integer $P$.

      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R$ ?

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, in very restricted settings.
      Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}
      Consider the routage graph ${\cal R}$ given in the previous subsection. 
      For each pair of routes $r_i$ and $r_j$, $v$ the first vertex which belongs to both routes,
      we set $\lambda(v,r_i) - \lambda(v,r_j)$ to $P$ instead of $1$. We chose $P$ to be an odd number smaller than $c$ the number of routes in ${\cal R}$. If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $T$ is the set of RRH. 
      We denote by $n$ the size of $S$ and $T$. We are given a period $P$, a message size $\tau$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH. Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$. Let consider a $(P,\tau)$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to 
      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.

@@

      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.

@@

@@

      Thus, the whole proccess time for a message sent at vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
      $$

    The {\bf maximum process time} of the $P$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.

@@

      \noindent {\bf Input:}  a matching $\rho$ from $L$ to $S$ two disjoint set of elements, a routage graph $\cal R$ whose set of sources is $S$ and whose set of targets is $T$, a period $P$, an integer $\tau$, an integer $T_{max}$.

@@

    \node (2) at (-7,-2){\Huge G};
    \node (3) at (10,-2){\Huge H};
    \end{tikzpicture}
